---
title: "Data Import"
output: github_document
---

```{r}
library(tidyverse)
library(readxl)
library(haven)
```

## Data Import: CSVs

Let's import data usig the 'readr' package.

```{r}
litters_df = read_csv("data/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

Look at the data

```{r}
litters_df

head(litters_df)
tail(litters_df)
```

View data in new window:
```{r, eval = FALSE}
view(litters_df)
#Causes issues when knitting. Don't include in final code if not needed, but helpful for viewing data.
```

```{r}
skimr::skim(litters_df)
```

'read_csv' options..
```{r, eval = FALSE}
read_csv("data/FAS_litters.csv", na = c("", "NA" , 999, 88), skip = 2)
```

## Data Import: Other file formats

We need to read in an excel spreadsheet. Load readxl library first.

```{r}
library(readxl)
```


```{r}
mlb_df = read_excel("data/mlb11.xlsx")
```

```{r, eval = FALSE}
View(mlb_df)
```

Read in specific cells from an excel sheet:
```{r}
lotr_words_df =
  read_excel(
    "data/LotR_Words.xlsx",
    range = "B3:D6")
```

## Still more formats

Read in a SAS dataset.

```{r}
library(haven)
```

```{r}
pulse_df = read_sas("data/public_pulse_data.sas7bdat")
```

## Data export
Create new folder named results on computer. Export df as a csv in this folder:
```{r}
write_csv(lotr_words_df, file = "results/lotr_words_df.csv")
```

## Why not base r??

```{r}
dont_do_this_df = read_csv("data/FAS_litters.csv")
#Prints results weird
```

